Live probes for free

### 2023-07-11 paper/example-programming.tex
Start to add ref

\section{Evaluation}
\label{sec:evaluation}
\section{Related Work}
\label{sec:related-work}
\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Evaluation}
\label{sec:evaluation}
\subsection{Demo : A Small C Live Programming Environment}
\label{sec:demo-small-c}
\subsection{Performance}
\label{sec:performance}
\section{Related Work}
\label{sec:related-work}

Example-Based Live Programming for Everyone\cite{10.1145/3426428.3426919} : Use GraalVM/Truffle to get live information from the code of multiple languages.

Example Centric Programming\cite{10.1145/1052883.1052894} : Use BeanShell(custom JVM) to get live information. Prototype for Java in Eclipse.

Usable Live Programming\cite{10.1145/2509578.2509585} : New language for live programming(Ying Yang) with incremental compilation. Live programming environment for this language.
Use source location to relate execution and code(=> almost like stack recording that link stackframe and code location)

Scalable Omniscient Debugging\cite{10.1145/1297105.1297067} : Omniscient debugging with a lot of data. Use a lot of memory to store all the data.
In this paper they record almost everything, we only record the stackframe.

\section{Conclusion}
\label{sec:conclusion}
